Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-01-31 src/tex/acknowledgments_contributions.tex
address comment #8
add coding font style for bioverse

\begin{acknowledgments}
\section*{Acknowledgments}
    The authors thank Kevin Heng, Dominik Hintz, and Rhys Seeburger for insightful discussions.
%    We are grateful to ...
%    mention any people who gave comments in early-on meetings
%    We thank the anonymous referees for providing insightful reports that helped to improve this manuscript.
    This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
    The results reported herein benefited from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
    This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
    T.L. was supported by the Branco Weiss Foundation, the Netherlands eScience Center (PROTEUS project, NLESC.OEC.2023.017), and the Alfred P. Sloan Foundation (AEThER project, G202114194).
%    ...
\end{acknowledgments}

\section*{Author contributions}
M.S., D.A., and S.R.\ conceived the project, planned its implementation, and interpreted the results.
M.S.\ developed the planetary evolution component to Bioverse, carried out the hypothesis tests and statistical analyses, and wrote the manuscript.
D.A.\ leads the ``Alien Earths'' program through which this project is funded, helped to guide the strategy of the project, and provided text contributions.
A.A.\ carried out the semi-analytical computations regarding the correlation of past UV flux and biosignature occurrence.
S.R.\ advised on planetary \gls{NUV} flux evolution and the cyanosulfidic scenario of the origins of life.
R.F.\ wrote the initial draft of the Introduction and advised on the evolutionary biology aspects of the project.
K.H.-U.\ contributed to the Bioverse software development and simulations.
%M.S.\ wrote the manuscript; ... and ... provided text contributions.
T.L.\ supported the selection of testable hypotheses and provided text contributions to the initial draft.
S.M.\ advised on the scope of the project and supported the selection of testable hypotheses.
All authors provided comments and suggestions on the manuscript.

>>>>

\begin{acknowledgments}
\section*{Acknowledgments}
    The authors thank Kevin Heng, Dominik Hintz, and Rhys Seeburger for insightful discussions.
%    We are grateful to ...
%    mention any people who gave comments in early-on meetings
%    We thank the anonymous referee for providing insightful reports that helped to improve this manuscript.
    This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
    The results reported herein benefited from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
    This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
    T.L. was supported by the Branco Weiss Foundation, the Netherlands eScience Center (PROTEUS project, NLESC.OEC.2023.017), and the Alfred P. Sloan Foundation (AEThER project, G202114194).
%    ...
\end{acknowledgments}

\section*{Author contributions}
M.S., D.A., and S.R.\ conceived the project, planned its implementation, and interpreted the results.
M.S.\ developed the planetary evolution component to \bioverse, carried out the hypothesis tests and statistical analyses, and wrote the manuscript.
D.A.\ leads the ``Alien Earths'' program through which this project is funded, helped to guide the strategy of the project, and provided text contributions.
A.A.\ carried out the semi-analytical computations regarding the correlation of past UV flux and biosignature occurrence.
S.R.\ advised on planetary \gls{NUV} flux evolution and the cyanosulfidic scenario of the origins of life.
R.F.\ wrote the initial draft of the Introduction and advised on the evolutionary biology aspects of the project.
K.H.-U.\ contributed to the \bioverse\ software development and simulations.
%M.S.\ wrote the manuscript; ... and ... provided text contributions.
T.L.\ supported the selection of testable hypotheses and provided text contributions to the initial draft.
S.M.\ advised on the scope of the project and supported the selection of testable hypotheses.
All authors provided comments and suggestions on the manuscript.

### 2025-01-31 src/tex/ms.tex
add coding font style for bioverse

\begin{abstract}
A wide variety of scenarios for the origin of life have been proposed, with many influencing the prevalence and distribution of biosignatures across exoplanet populations.
This relationship suggests these scenarios can be tested by predicting biosignature distributions and comparing them with empirical data.
Here, we demonstrate this approach by focusing on the cyanosulfidic origins-of-life scenario and investigating the hypothesis that a minimum near-ultraviolet (NUV) flux is necessary for abiogenesis.
Using Bayesian modeling and the Bioverse survey simulator, we constrain the probability of obtaining strong evidence for or against this ``UV Threshold Hypothesis'' with future biosignature surveys.
Our results indicate that a correlation between past NUV flux and current biosignature occurrence is testable for sample sizes of $\gtrsim$50 planets.
The diagnostic power of such tests is critically sensitive to the intrinsic abiogenesis rate and host star properties, particularly maximum past NUV fluxes.
Surveys targeting a wide range of fluxes, and planets orbiting M dwarfs enhance the chances of conclusive results, with sample sizes $\gtrsim$100 providing $\gtrsim$80\% likelihood of strong evidence if abiogenesis rates are high and the required NUV fluxes are moderate.
For required fluxes exceeding a few hundred erg/s/cm$^2$, both the fraction of inhabited planets and the diagnostic power sharply decrease.
Our findings demonstrate the potential of exoplanet surveys to test origins-of-life hypotheses.
 Beyond specific scenarios, this work underscores the broader value of realistic survey simulations for future observatories (e.g., HWO, LIFE, ELTs, Nautilus) in identifying testable science questions, optimizing mission strategies, and advancing theoretical and experimental studies of abiogenesis.
% This approach emphasizes the need to contextualize biosignature detections, enhancing their credibility and offering new approaches to explore the emergence of life on Earth and beyond.
\end{abstract}

@@

A real exoplanet survey will be subject to observational biases and sample selection effects, and will be constrained by the underlying demographics of the planet sample.
To assess the information gain of a realistic exoplanet survey, we employed Bioverse~\citep{Bixel2021,Hardegree-Ullman2023,Schlecker2024,Hardegree-Ullman2024}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a hypothesis testing module to evaluate the statistical power of different observational strategies.

@@

This paper is organized as follows:
In Section~\ref{sec:methods}, we introduce both our semi-analytical approach and Bioverse simulations for testing the UV Threshold Hypothesis.
Section~\ref{sec:results} presents the results of these experiments for a generic survey as well as for a realistic transit survey.
In Section~\ref{sec:discussion}, we discuss our findings before concluding with a summary in Section~\ref{sec:conclusions}.

@@

\subsection{Exoplanet survey simulations with Bioverse}
To assess the diagnostic power of realistic exoplanet surveys, we employed our survey simulator and hypothesis testing framework Bioverse~\citep{Bixel2021}.
The general approach is as follows:
\begin{enumerate}
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics~\citep{Bergsten2022,Hardegree-Ullman2023}.
Here, we also inject the demographic trend in question - in this case we assign biosignatures according to $H_1$, i.e., to planets in the \gls{HZ} that have received \gls{NUV} fluxes above a certain threshold.
    \item \textbf{Survey simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with Bioverse using different sample sizes and survey strategies.
    \item \textbf{Hypothesis testing:} We evaluate the likelihood that a given survey would detect a specified demographic trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
    A common definition of the null hypothesis $H_\mathrm{null}$, which is also applied here, is that there is no relationship between the independent variable (here: maximum NUV flux) and the dependent variable (here: biosignature occurrence).
    The alternative hypothesis $H_1$ proposes a specific relationship between the independent and dependent variables.
    Bioverse offers either Bayesian model comparison or non-parametric tests to evaluate the evidence for or against the null hypothesis.
\end{enumerate}

To determine the diagnostic capability of a given survey, Bioverse runs multiple iterations of the simulated survey and calculates the fraction of realizations that successfully reject the null hypothesis.
We used this metric, known as the statistical power, to quantify the potential information content of the survey, identify critical design trades, and find strategies that maximize the survey's scientific return.
% TODO: IF INFERENCE: add:
%The posterior samples obtained from the nested sampling runs further allows us to estimate the precision with which the survey could constrain the parameters of the hypothesized trend.

@@

\subsubsection{Transit survey simulations}
With the synthetic star and planet samples generated, we used Bioverse's survey module to simulate noisy measurements of key observables with a transit survey.
We assumed a hypothetical mission that can target a large planet sample with high photometric precision and conduct a biosignature search on these planets~\citep[e.g.,][]{Apai2019,Apai2022}.
The simulated survey was designed to measure planetary instellation (for \gls{HZ} occupancy) with a precision of \var{nautilus_S} and host star effective temperature with a precision of \var{nautilus_T_eff_st}~K.
The maximum past \gls{NUV} flux a planet received can be determined within a precision of \var{nautilus_max_nuv}.
To marginalize over choices of biosignatures and their detectability, which are beyond the scope of this study, we assumed that any inhabited planet would show a biosignature detectable by the survey.

@@

\subsubsection{Hypothesis testing}
%To evaluate the evidence for correctly rejecting the null hypothesis, we employed the Mann-Whitney U test~\citep{Mann1947}.
\rev{We ought to choose a statistical test that is sensitive to the UV~Threshold Hypothesis, and that could be realistically conducted in a future transit survey (which may include auxiliary information from ground-based observations, archived data, or models).
Given the available types of data expected from such surveys, our test shall be non-parametric and compare two samples -- planets with and without biosignatures -- to assess whether they are drawn from the same underlying population in terms of their infered historic maximum NUV flux.
Common options include the Kolmogorov-Smirnov test, the Brunner-Munzel test~\citep{Brunner2000}, and the Mann-Whitney U test~\citep{Mann1947}.
Due to its availability and suitability for large sample sizes, we chose the Mann-Whitney U test, which evaluates if one sample is stochastically greater than the other.
Here, we }
compare the distributions of \gls{NUV} fluxes of planets with and without biosignatures.
The implementation in Bioverse relies on the \texttt{scipy.stats.mannwhitneyu} function~\citep{Virtanen2020} and returns a p-value \rev{for each test.
To balance the trade-off between Type I and Type II error risks, we set the significance level to the widely adopted threshold $\alpha = 0.05$.
%This choice ensures a reasonable trade-off between detecting a potential dependence of biosignatures on NUV flux while controlling for statistical noise.
To quantify the diagnostic power of the survey, we conducted repeated randomized realizations and calculated the fraction of successful rejections of the null hypothesis, i.e., the statistical power.
}

@@

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}
%\begin{figure}
%    \script{inhabited_FGKM.py}
%    \begin{centering}
%        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
%        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
%        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
%        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
%        }
%        \label{fig:inhabited_FGKM}
%    \end{centering}
%\end{figure}
%In a magnitude- and volume-limited sample of a transit survey, the host star distribution for \glspl{EEC} will be skewed toward later spectral types and dominated by M~dwarfs due to how the \gls{HZ} scales with spectral type.
With \gls{HZ} occupancy as a requirement for abiogenesis, and barring selection biases beyond stellar brightness, the host star distribution of inhabited planets in a simulated transit survey is skewed toward later spectral types.
For a fixed planet sample size, the fraction of inhabited planets is highest for planets orbiting M~dwarfs due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars (see Figures~\ref{fig:hz_nuv_evo},~\ref{fig:surveys_FGKM}).
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (see Equation~\ref{eq:hypothesis-uv}).
Thus -- under the UV Threshold Hypothesis -- most inhabited transiting planets in the sample orbit M~dwarfs.

@@

%The particular finding that our future observer might prefer to prioritize extreme values of this variable in order to maximize statistical power.
The particular finding that prioritizing extreme values of past \gls{NUV} flux can enhance statistical power likely clashes with observational constraints, as the composition of the subset of planets that we can observe and for which detection of biosignature can be attempted is not independent from their \gls{NUV} flux history.
Hence, for our future observer, selectivity and sample size may be in conflict.
This trade-off can be quantified in terms of expected evidence yield, which we have done in Section~\ref{sec:results-semianalytical}.
Our analysis shows that regardless of selectivity, sample sizes smaller than 50 likely result in inconclusive tests, and that increasing selectivity towards extreme $F_{\mathrm{NUV}}$ offers limited inference gains compared to the uniform case ($s=0$; Figure~\ref{fig:semian_selectivity}).
For larger samples, however, a narrow distribution of $F_{\mathrm{NUV}}$ may prevent inference entirely.
We thus argue that selecting a sample with $F_{\mathrm{NUV}}$ distributed uniformly or emphasizing extreme values should -- barring any practical counterarguments -- be considered in any future attempt at testing the UV~Threshold Hypothesis.
Since the practical implementation of an exoplanet survey can stand in the way of such a selection, the following discussion focuses on the results of our transit survey simulations with Bioverse.

@@

\subsection{Sensitivity to astrophysical parameters} % corresponds to conclusion point 3
Our Bioverse simulations that take into account exoplanet demographics, the evolution of habitability and \gls{NUV} fluxes, and observational biases show that not only the likelihood of a conclusive test of the UV~Threshold Hypothesis, but also the likelihood of successful biosignature detection itself is extremely sensitive to the threshold \gls{NUV} flux if the hypothesis is true.
Even if all biosignatures can be detected and the nominal \rev{rate of life's emergence and persistence} is very high, say $f_\mathrm{life} = 1$, under the condition that prebiotic chemistry requires a minimum \gls{NUV} flux \textit{and} liquid water, if the threshold flux turns out to be high the probability of finding life on a randomly selected planet may be very low.
As we showed, for high required fluxes the two requirements of simultaneous \gls{HZ} occupancy and sufficient \gls{NUV} flux conspire to diminish the fraction of inhabited planets in the sample.
Taking the inferred fluxes from \citet{Richey-Yowell2023} at face value (but taking into account intrinsic scatter), a minimum required \gls{NUV} flux of $\gtrsim\SI{400}{\erg\per\second\per\centi\meter\squared}$ reduces the fraction of inhabited planets to below $\sim\SI{1}{\percent}$.
This not only calls for a large sample size and a targeted sample selection preferring high expected past \gls{NUV} fluxes, but also highlight the necessity of continued theoretical and experimental research into the role of \gls{UV} radiation in prebiotic chemistry~\citep{Ranjan2017b,Rimmer2018,Rimmer2021}.

@@

\subsection{Overall prospects for testing the UV~Threshold Hypothesis} % corresponds to conclusion point 4
Our results show that the UV~Threshold Hypothesis is testable with potential future exoplanet surveys, but that the success of such a test depends on the sample size, the distribution of past \gls{NUV} fluxes, and several unknown astrophysical nuisance parameters.
Even under idealized conditions, obtaining strong evidence for or against the hypothesis likely requires sample sizes on the order of 100 (see Section~\ref{sec:results-semianalytical}).
This is true for a future transit survey, the specifics of which we have reflected in our Bioverse simulations (see Section~\ref{sec:results-bioverse}).
However, we have shown that the impacts from the combined requirements of the UV~Threshold Hypothesis on the fraction of inhabited planets in a sample are comparable in the non-transiting case.
%The projected planet yield of most currently planned exoplanet mission concepts are likely insufficient to test the UV~Threshold Hypothesis:

Given the challenging nature of detecting and characterizing small (Earth-sized) exoplanets, most exoplanet mission concepts currently under development or considered lack the potential for characterizing large enough samples.
Ground-based 25--40-meter class extremely large telescopes are expected to have the capabilities to detect biosignatures on exoplanets like Proxima Centauri~b~\citep[e.g.,][]{Wang2017,Hawker2019,Zhang2024,Vaughan2024}.
\citet{Hardegree-Ullman2024} used Bioverse to determine potential yields for a 10-year direct imaging and high-resolution spectroscopy survey of O$_2$ on the Giant Magellan Telescope (GMT) and on the Extremely Large Telescope (ELT) and found that between 7 and 19 habitable zone Earth-sized planets could be probed for Earth-like oxygen levels.
Such a sample is too small to test the UV Threshold Hypothesis, but it may be synergistic with other detection methods.

@@

\section{Conclusions}
\label{sec:conclusions}
We propose that specific origins-of-life scenarios may leave a detectable imprint on the distribution of biosignatures in exoplanet populations.
We have investigated the potential of upcoming exoplanet surveys to test the hypothesis -- motivated by the cyanosulfidic origins-of-life scenario -- that a minimum past \gls{NUV} flux is required for abiogenesis.
To this end, we first employed a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against this hypothesis.
We then used the Bioverse framework to assess the diagnostic power of realistic transit surveys, taking into account exoplanet demographics, time-dependency of habitability and \gls{NUV} fluxes, observational biases, and target selection.

>>>>

\begin{abstract}
A wide variety of scenarios for the origin of life have been proposed, with many influencing the prevalence and distribution of biosignatures across exoplanet populations.
This relationship suggests these scenarios can be tested by predicting biosignature distributions and comparing them with empirical data.
Here, we demonstrate this approach by focusing on the cyanosulfidic origins-of-life scenario and investigating the hypothesis that a minimum near-ultraviolet (NUV) flux is necessary for abiogenesis.
Using Bayesian modeling and the \bioverse\ survey simulator, we constrain the probability of obtaining strong evidence for or against this ``UV Threshold Hypothesis'' with future biosignature surveys.
Our results indicate that a correlation between past NUV flux and current biosignature occurrence is testable for sample sizes of $\gtrsim$50 planets.
The diagnostic power of such tests is critically sensitive to the intrinsic abiogenesis rate and host star properties, particularly maximum past NUV fluxes.
Surveys targeting a wide range of fluxes, and planets orbiting M dwarfs enhance the chances of conclusive results, with sample sizes $\gtrsim$100 providing $\gtrsim$80\% likelihood of strong evidence if abiogenesis rates are high and the required NUV fluxes are moderate.
For required fluxes exceeding a few hundred erg/s/cm$^2$, both the fraction of inhabited planets and the diagnostic power sharply decrease.
Our findings demonstrate the potential of exoplanet surveys to test origins-of-life hypotheses.
 Beyond specific scenarios, this work underscores the broader value of realistic survey simulations for future observatories (e.g., HWO, LIFE, ELTs, Nautilus) in identifying testable science questions, optimizing mission strategies, and advancing theoretical and experimental studies of abiogenesis.
% This approach emphasizes the need to contextualize biosignature detections, enhancing their credibility and offering new approaches to explore the emergence of life on Earth and beyond.
\end{abstract}

@@

A real exoplanet survey will be subject to observational biases and sample selection effects, and will be constrained by the underlying demographics of the planet sample.
To assess the information gain of a realistic exoplanet survey, we employed \bioverse~\citep{Bixel2021,Hardegree-Ullman2023,Schlecker2024,Hardegree-Ullman2024}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a hypothesis testing module to evaluate the statistical power of different observational strategies.

@@

This paper is organized as follows:
In Section~\ref{sec:methods}, we introduce both our semi-analytical approach and \bioverse\ simulations for testing the UV Threshold Hypothesis.
Section~\ref{sec:results} presents the results of these experiments for a generic survey as well as for a realistic transit survey.
In Section~\ref{sec:discussion}, we discuss our findings before concluding with a summary in Section~\ref{sec:conclusions}.

@@

\subsection{Exoplanet survey simulations with \bioverse}
To assess the diagnostic power of realistic exoplanet surveys, we employed our survey simulator and hypothesis testing framework \bioverse~\citep{Bixel2021}.
The general approach is as follows:
\begin{enumerate}
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics~\citep{Bergsten2022,Hardegree-Ullman2023}.
Here, we also inject the demographic trend in question - in this case we assign biosignatures according to $H_1$, i.e., to planets in the \gls{HZ} that have received \gls{NUV} fluxes above a certain threshold.
    \item \textbf{Survey simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with \bioverse\ using different sample sizes and survey strategies.
    \item \textbf{Hypothesis testing:} We evaluate the likelihood that a given survey would detect a specified demographic trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
    A common definition of the null hypothesis $H_\mathrm{null}$, which is also applied here, is that there is no relationship between the independent variable (here: maximum NUV flux) and the dependent variable (here: biosignature occurrence).
    The alternative hypothesis $H_1$ proposes a specific relationship between the independent and dependent variables.
    \bioverse\ offers either Bayesian model comparison or non-parametric tests to evaluate the evidence for or against the null hypothesis.
\end{enumerate}

To determine the diagnostic capability of a given survey, \bioverse\ runs multiple iterations of the simulated survey and calculates the fraction of realizations that successfully reject the null hypothesis.
We used this metric, known as the statistical power, to quantify the potential information content of the survey, identify critical design trades, and find strategies that maximize the survey's scientific return.
% TODO: IF INFERENCE: add:
%The posterior samples obtained from the nested sampling runs further allows us to estimate the precision with which the survey could constrain the parameters of the hypothesized trend.

@@

\subsubsection{Transit survey simulations}
With the synthetic star and planet samples generated, we used \bioverse's survey module to simulate noisy measurements of key observables with a transit survey.
We assumed a hypothetical mission that can target a large planet sample with high photometric precision and conduct a biosignature search on these planets~\citep[e.g.,][]{Apai2019,Apai2022}.
The simulated survey was designed to measure planetary instellation (for \gls{HZ} occupancy) with a precision of \var{nautilus_S} and host star effective temperature with a precision of \var{nautilus_T_eff_st}~K.
The maximum past \gls{NUV} flux a planet received can be determined within a precision of \var{nautilus_max_nuv}.
To marginalize over choices of biosignatures and their detectability, which are beyond the scope of this study, we assumed that any inhabited planet would show a biosignature detectable by the survey.

@@

\subsubsection{Hypothesis testing}
%To evaluate the evidence for correctly rejecting the null hypothesis, we employed the Mann-Whitney U test~\citep{Mann1947}.
\rev{We ought to choose a statistical test that is sensitive to the UV~Threshold Hypothesis, and that could be realistically conducted in a future transit survey (which may include auxiliary information from ground-based observations, archived data, or models).
Given the available types of data expected from such surveys, our test shall be non-parametric and compare two samples -- planets with and without biosignatures -- to assess whether they are drawn from the same underlying population in terms of their infered historic maximum NUV flux.
Common options include the Kolmogorov-Smirnov test, the Brunner-Munzel test~\citep{Brunner2000}, and the Mann-Whitney U test~\citep{Mann1947}.
Due to its availability and suitability for large sample sizes, we chose the Mann-Whitney U test, which evaluates if one sample is stochastically greater than the other.
Here, we }
compare the distributions of \gls{NUV} fluxes of planets with and without biosignatures.
The implementation in \bioverse\ relies on the \texttt{scipy.stats.mannwhitneyu} function~\citep{Virtanen2020} and returns a p-value \rev{for each test.
To balance the trade-off between Type I and Type II error risks, we set the significance level to the widely adopted threshold $\alpha = 0.05$.
%This choice ensures a reasonable trade-off between detecting a potential dependence of biosignatures on NUV flux while controlling for statistical noise.
To quantify the diagnostic power of the survey, we conducted repeated randomized realizations and calculated the fraction of successful rejections of the null hypothesis, i.e., the statistical power.
}

@@

\subsection{Survey simulations with \bioverse}\label{sec:results-bioverse}
%\begin{figure}
%    \script{inhabited_FGKM.py}
%    \begin{centering}
%        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
%        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
%        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
%        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
%        }
%        \label{fig:inhabited_FGKM}
%    \end{centering}
%\end{figure}
%In a magnitude- and volume-limited sample of a transit survey, the host star distribution for \glspl{EEC} will be skewed toward later spectral types and dominated by M~dwarfs due to how the \gls{HZ} scales with spectral type.
With \gls{HZ} occupancy as a requirement for abiogenesis, and barring selection biases beyond stellar brightness, the host star distribution of inhabited planets in a simulated transit survey is skewed toward later spectral types.
For a fixed planet sample size, the fraction of inhabited planets is highest for planets orbiting M~dwarfs due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars (see Figures~\ref{fig:hz_nuv_evo},~\ref{fig:surveys_FGKM}).
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (see Equation~\ref{eq:hypothesis-uv}).
Thus -- under the UV Threshold Hypothesis -- most inhabited transiting planets in the sample orbit M~dwarfs.

@@

%The particular finding that our future observer might prefer to prioritize extreme values of this variable in order to maximize statistical power.
The particular finding that prioritizing extreme values of past \gls{NUV} flux can enhance statistical power likely clashes with observational constraints, as the composition of the subset of planets that we can observe and for which detection of biosignature can be attempted is not independent from their \gls{NUV} flux history.
Hence, for our future observer, selectivity and sample size may be in conflict.
This trade-off can be quantified in terms of expected evidence yield, which we have done in Section~\ref{sec:results-semianalytical}.
Our analysis shows that regardless of selectivity, sample sizes smaller than 50 likely result in inconclusive tests, and that increasing selectivity towards extreme $F_{\mathrm{NUV}}$ offers limited inference gains compared to the uniform case ($s=0$; Figure~\ref{fig:semian_selectivity}).
For larger samples, however, a narrow distribution of $F_{\mathrm{NUV}}$ may prevent inference entirely.
We thus argue that selecting a sample with $F_{\mathrm{NUV}}$ distributed uniformly or emphasizing extreme values should -- barring any practical counterarguments -- be considered in any future attempt at testing the UV~Threshold Hypothesis.
Since the practical implementation of an exoplanet survey can stand in the way of such a selection, the following discussion focuses on the results of our transit survey simulations with \bioverse.

@@

\subsection{Sensitivity to astrophysical parameters} % corresponds to conclusion point 3
Our \bioverse\ simulations that take into account exoplanet demographics, the evolution of habitability and \gls{NUV} fluxes, and observational biases show that not only the likelihood of a conclusive test of the UV~Threshold Hypothesis, but also the likelihood of successful biosignature detection itself is extremely sensitive to the threshold \gls{NUV} flux if the hypothesis is true.
Even if all biosignatures can be detected and the nominal \rev{rate of life's emergence and persistence} is very high, say $f_\mathrm{life} = 1$, under the condition that prebiotic chemistry requires a minimum \gls{NUV} flux \textit{and} liquid water, if the threshold flux turns out to be high the probability of finding life on a randomly selected planet may be very low.
As we showed, for high required fluxes the two requirements of simultaneous \gls{HZ} occupancy and sufficient \gls{NUV} flux conspire to diminish the fraction of inhabited planets in the sample.
Taking the inferred fluxes from \citet{Richey-Yowell2023} at face value (but taking into account intrinsic scatter), a minimum required \gls{NUV} flux of $\gtrsim\SI{400}{\erg\per\second\per\centi\meter\squared}$ reduces the fraction of inhabited planets to below $\sim\SI{1}{\percent}$.
This not only calls for a large sample size and a targeted sample selection preferring high expected past \gls{NUV} fluxes, but also highlight the necessity of continued theoretical and experimental research into the role of \gls{UV} radiation in prebiotic chemistry~\citep{Ranjan2017b,Rimmer2018,Rimmer2021}.

@@

\subsection{Overall prospects for testing the UV~Threshold Hypothesis} % corresponds to conclusion point 4
Our results show that the UV~Threshold Hypothesis is testable with potential future exoplanet surveys, but that the success of such a test depends on the sample size, the distribution of past \gls{NUV} fluxes, and several unknown astrophysical nuisance parameters.
Even under idealized conditions, obtaining strong evidence for or against the hypothesis likely requires sample sizes on the order of 100 (see Section~\ref{sec:results-semianalytical}).
This is true for a future transit survey, the specifics of which we have reflected in our \bioverse\ simulations (see Section~\ref{sec:results-bioverse}).
However, we have shown that the impacts from the combined requirements of the UV~Threshold Hypothesis on the fraction of inhabited planets in a sample are comparable in the non-transiting case.
%The projected planet yield of most currently planned exoplanet mission concepts are likely insufficient to test the UV~Threshold Hypothesis:

Given the challenging nature of detecting and characterizing small (Earth-sized) exoplanets, most exoplanet mission concepts currently under development or considered lack the potential for characterizing large enough samples.
Ground-based 25--40-meter class extremely large telescopes are expected to have the capabilities to detect biosignatures on exoplanets like Proxima Centauri~b~\citep[e.g.,][]{Wang2017,Hawker2019,Zhang2024,Vaughan2024}.
\citet{Hardegree-Ullman2024} used \bioverse\ to determine potential yields for a 10-year direct imaging and high-resolution spectroscopy survey of O$_2$ on the Giant Magellan Telescope (GMT) and on the Extremely Large Telescope (ELT) and found that between 7 and 19 habitable zone Earth-sized planets could be probed for Earth-like oxygen levels.
Such a sample is too small to test the UV Threshold Hypothesis, but it may be synergistic with other detection methods.

@@

\section{Conclusions}
\label{sec:conclusions}
We propose that specific origins-of-life scenarios may leave a detectable imprint on the distribution of biosignatures in exoplanet populations.
We have investigated the potential of upcoming exoplanet surveys to test the hypothesis -- motivated by the cyanosulfidic origins-of-life scenario -- that a minimum past \gls{NUV} flux is required for abiogenesis.
To this end, we first employed a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against this hypothesis.
We then used the \bioverse\ framework to assess the diagnostic power of realistic transit surveys, taking into account exoplanet demographics, time-dependency of habitability and \gls{NUV} fluxes, observational biases, and target selection.
